Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-19 paper.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Models are largely employed in the science and engineering areas, in order to analyze, predict, and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many engineering advances, in the last centuries. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions \cite{stochmodel}. Nonetheless, one can argue that such models are not enough to represent, CPSs since the interaction among software, communications, and hardware presents a lot of events that could not be deterministically or stochastically modeled and may be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, early representations of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in instantiating discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which may even be negligible. On the other hand, that approach is not suitable for complex CPSs that present intense nondeterminism, where uncertainties play a central role and may in validate the entire system behavior.

@@

In addition, Shoukry {\it et. al} \cite{Shoukry} tackled another important problem related to CPSs: security. Indeed, the very essence of CPSs claim for sophisticated interfacing ({\it e.g.}, sensors and network connections), which normally leads to security issues \cite{cpsattack}, given that wrong control actions may be generated based on corrupted measurements. The mentioned authors proposed a methodology for estimating the state of physical systems, through formal methods, even if sensor inputs are contaminated with erroneous or intentionally corrupted data, in order to still be able to execute suitable control commands. Indeed, many situations may be regarded as satisfiability problems and solved, for instance, with approaches based on Satisfiability Modulo Theories (SMT) \cite{Araujo16} \textcolor{red}{eh bom citar mais}, which indicates many links with other research areas and may lead to a unified approach regarding system verification, security enforcement, and interaction handling.

>>>>

Models are largely employed in science and engineering areas, in order to analyze, predict, and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many recent engineering advances. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions~\cite{stochmodel}. Nonetheless, one can argue that such models are not enough to represent CPSs since the interaction among different entities (software and hardware components) presents several events that could not be deterministically or stochastically modeled; they can be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, early representations of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in instantiating discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which can even be negligible. On the other hand, that approach is not suitable for complex CPSs that present intense nondeterminism, where uncertainties play a central role and might invalidate the entire system behavior.

@@

In addition, Shoukry {\it et. al} \cite{Shoukry} tackled another important problem related to CPSs: security. Indeed, the essence of CPSs claims for sophisticated interfacing ({\it e.g.}, sensors and network connections), which normally leads to security issues~\cite{cpsattack}, given that wrong control actions can be generated based on corrupted measurements. The mentioned authors proposed a methodology for estimating the state of physical systems, through formal methods, even if sensor inputs are contaminated with erroneous or intentionally corrupted data, in order to still be able to execute suitable control commands. Indeed, many situations can be regarded as satisfiability problems and solved, for instance, with approaches based on Satisfiability Modulo Theories (SMT)~\cite{Araujo16} \textcolor{red}{eh bom citar mais}, which indicates many links with other research areas and might lead to a unified approach regarding system verification, security enforcement, and interaction handling.
